### 2008-09-10 developments/HARDWARE_LIBRARY/PDB/BIT_DEFINITION.tex

\hspace*{0.20in}\it BIT\_VECTOR\_DEFINITION

\vspace*{4mm}
\bf SEES

@@

\hspace*{0.20in}\it BIT\_VECTOR\rm ,

\hspace*{0.20in}\it bv\_size\rm , \it bv\_catenate\rm , \it bv\_sub\rm , \it bv\_zero\rm , \it bv\_one\rm ,

\hspace*{0.20in}\it bv\_not\rm ,\hspace*{0.20in}\it bv\_and\rm ,\hspace*{0.20in}\it bv\_or\rm , \it bv\_xor\rm ,

\hspace*{0.20in}\it bv\_at\rm , \it bv\_set\rm , \it bv\_clear

@@

\hspace*{0.20in}\it BIT\_VECTOR \rm = \bf seq1 \rm (\it BIT\rm )  $\land$

\vspace*{4mm}
\hspace*{0.20in}\it bv\_size  $\in$  \it BIT\_VECTOR  $\fun$   $ \na1 $   $\land$

\hspace*{0.20in}\it bv\_size \rm =  $\lambda$ \rm (\it bv\rm )\rm .\rm (\it bv  $\in$  \it BIT\_VECTOR  $\mid$  \bf size\rm (\it bv\rm )\rm )  $\land$

\vspace*{4mm}
\hspace*{0.20in}\it bv\_catenate  $\in$  \it BIT\_VECTOR  $\times$  \it BIT\_VECTOR  $\fun$  \it BIT\_VECTOR  $\land$

\hspace*{0.20in}\it bv\_catenate \rm =  $\lambda$ \rm (\it v1\rm ,\it v2\rm ) \rm . \rm (\it v1  $\in$  \it BIT\_VECTOR  $\land$  \it v2 $\in$  \it BIT\_VECTOR  $\mid$  \it v2  $\cat$  \it v1\rm )  $\land$

\vspace*{4mm}
\hspace*{0.20in}\it bv\_sub  $\in$  \it BIT\_VECTOR  $\times$   $\nat$   $\times$   $\nat$   $\fun$  \it BIT\_VECTOR  $\land$

\hspace*{0.20in}\it bv\_sub \rm =  $\lambda$ \rm (\it bv\rm , \it low\rm , \it high\rm ) \rm . \rm (\it bv  $\in$  \it BIT\_VECTOR  $\land$  \it low $\in$   $\nat$   $\land$  \it high $\in$   $\nat$   $\land$  \it low  $\leq$  \it high  $\mid$  \rm 0 $\upto$ \rm (\it high\rm -\it low\rm )  $\dres$  \it bv\rm )  $\land$

\vspace*{4mm}
\hspace*{0.20in}\it bv\_zero  $\in$   $ \na1 $   $\fun$  \it BIT\_VECTOR  $\land$

\hspace*{0.20in}\it bv\_zero \rm =  $\lambda$ \rm (\it sz\rm ) \rm . \rm (\it sz  $\in$   $ \na1 $   $\mid$  \rm (\rm 1 $\upto$ \it sz\rm )  $\times$  \rm \{\rm 0\rm \}\rm )  $\land$

\vspace*{4mm}
\hspace*{0.20in}\it bv\_one  $\in$   $ \na1 $   $\fun$  \it BIT\_VECTOR  $\land$

\hspace*{0.20in}\it bv\_one \rm =  $\lambda$ \rm (\it sz\rm ) \rm . \rm (\it sz  $\in$   $ \na1 $   $\mid$  \rm (\rm 1 $\upto$ \it sz\rm )  $\times$  \rm \{\rm 1\rm \}\rm )  $\land$

\vspace*{4mm}
\hspace*{0.20in}\it bv\_not  $\in$  \it BIT\_VECTOR  $\fun$  \it BIT\_VECTOR  $\land$

\hspace*{0.20in}\it bv\_not \rm =  $\lambda$ \rm (\it v1\rm )\rm .\rm (\it v1 $\in$  \it BIT\_VECTOR  $\mid$   $\lambda$ \rm (\it idx\rm )\rm .\rm (\it idx  $\in$  \rm 1 $\upto$ \bf size\rm (\it v1\rm )  $\mid$  \it bit\_not\rm (\it v1\rm (\it idx\rm )\rm )\rm )\rm )  $\land$

\vspace*{4mm}
\hspace*{0.20in}\it bv\_and  $\in$  \it BIT\_VECTOR  $\times$  \it BIT\_VECTOR  $\fun$  \it BIT\_VECTOR  $\land$

\hspace*{0.20in}\it bv\_and \rm =  $\lambda$ \rm (\it v1\rm ,\it v2\rm )\rm .\rm (\it v1 $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR  $\land$  \bf size\rm (\it v1\rm ) \rm = \bf size\rm (\it v2\rm )  $\mid$

\hspace*{0.40in} $\lambda$ \rm (\it idx\rm )\rm .\rm (\it idx  $\in$  \rm 1 $\upto$ \bf size\rm (\it v1\rm )  $\mid$  \it bit\_and\rm (\it v1\rm (\it idx\rm )\rm ,\it v2\rm (\it idx\rm )\rm )\rm )\rm )  $\land$

\vspace*{4mm}
\hspace*{0.20in}\it bv\_or  $\in$  \it BIT\_VECTOR  $\times$  \it BIT\_VECTOR  $\fun$  \it BIT\_VECTOR  $\land$

\hspace*{0.20in}\it bv\_or \rm =  $\lambda$ \rm (\it v1\rm ,\it v2\rm )\rm .\rm (\it v1 $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR  $\land$  \bf size\rm (\it v1\rm ) \rm = \bf size\rm (\it v2\rm )  $\mid$

\hspace*{0.40in} $\lambda$ \rm (\it idx\rm )\rm .\rm (\it idx  $\in$  \rm 1 $\upto$ \bf size\rm (\it v1\rm )  $\mid$  \it bit\_or\rm (\it v1\rm (\it idx\rm )\rm ,\it v2\rm (\it idx\rm )\rm )\rm )\rm )  $\land$

\vspace*{4mm}
\hspace*{0.20in}\it bv\_xor  $\in$  \it BIT\_VECTOR  $\times$  \it BIT\_VECTOR  $\fun$  \it BIT\_VECTOR  $\land$

\hspace*{0.20in}\it bv\_xor \rm =  $\lambda$ \rm (\it v1\rm ,\it v2\rm )\rm .\rm (\it v1 $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR  $\land$  \bf size\rm (\it v1\rm ) \rm = \bf size\rm (\it v2\rm )  $\mid$

\hspace*{0.40in} $\lambda$ \rm (\it idx\rm )\rm .\rm (\it idx  $\in$  \rm 1 $\upto$ \bf size\rm (\it v1\rm )  $\mid$  \it bit\_xor\rm (\it v1\rm (\it idx\rm )\rm ,\it v2\rm (\it idx\rm )\rm )\rm )\rm )  $\land$

\vspace*{4mm}
\hspace*{0.20in}\it bv\_at  $\in$  \it BIT\_VECTOR  $\times$   $\nat$   $\fun$  \it BIT  $\land$

\hspace*{0.20in}\it bv\_at \rm =  $\lambda$ \rm (\it v1\rm ,\it idx\rm )\rm .\rm (\it v1 $\in$  \it BIT\_VECTOR  $\land$  \it idx  $\in$   $\nat$   $\land$  \it idx $<$ \bf size\rm (\it v1\rm )  $\mid$  \it v1\rm (\it idx\rm +\rm 1\rm )\rm )  $\land$

\vspace*{4mm}
\hspace*{0.20in}\it bv\_set  $\in$  \it BIT\_VECTOR  $\times$   $\nat$   $\fun$  \it BIT\_VECTOR  $\land$

\hspace*{0.20in}\it bv\_set \rm =  $\lambda$ \rm (\it v1\rm ,\it idx\rm )\rm .\rm (\it v1 $\in$  \it BIT\_VECTOR  $\land$  \it idx  $\in$   $\nat$   $\land$  \it idx $<$ \bf size\rm (\it v1\rm )  $\mid$  \it v1  $\lover$  \rm \{ \it idx\rm +\rm 1  $\mapsto$  \rm 1 \rm \}\rm )  $\land$

\hspace*{0.20in}\it bv\_clear  $\in$  \it BIT\_VECTOR  $\times$   $\nat$   $\fun$  \it BIT\_VECTOR  $\land$

\hspace*{0.20in}\it bv\_clear \rm =  $\lambda$ \rm (\it v1\rm ,\it idx\rm )\rm .\rm (\it v1 $\in$  \it BIT\_VECTOR  $\land$  \it idx  $\in$   $\nat$   $\land$  \it idx $<$ \bf size\rm (\it v1\rm )  $\mid$  \it v1  $\lover$  \rm \{ \it idx\rm +\rm 1  $\mapsto$  \rm 0 \rm \}\rm )

@@

\hspace*{0.20in} $\forall$  \it bv\rm . \rm (\it bv  $\in$  \it BIT\_VECTOR  $\implies$  \it bv\_size\rm (\it bv\_not\rm (\it bv\rm )\rm ) \rm = \it bv\_size\rm (\it bv\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \it bv\rm . \rm (\it bv  $\in$  \it BIT\_VECTOR  $\implies$  \rm (\it bv\_not\rm (\it bv\_not\rm (\it bv\rm )\rm ) \rm = \it bv\rm )\rm )\rm ;

\vspace*{4mm}
\hspace*{0.20in} $\forall$  \rm (\it v1\rm ,\it v2\rm )\rm . \rm (\it v1  $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR  $\implies$

\hspace*{0.60in}\it bv\_size\rm (\it bv\_catenate\rm (\it v1\rm , \it v2\rm )\rm ) \rm = \it bv\_size\rm (\it v1\rm ) \rm + \it bv\_size\rm (\it v2\rm )\rm )\rm ;

\vspace*{4mm}
\hspace*{0.20in} $\forall$  \rm (\it bv\rm ,\it low\rm ,\it high\rm )\rm . \rm (\it bv  $\in$  \it BIT\_VECTOR  $\land$  \it low  $\in$   $\nat$   $\land$  \it high  $\in$   $\nat$   $\land$  \it low  $\leq$  \it high  $\implies$

\hspace*{0.60in}\it bv\_size\rm (\it bv\_sub\rm (\it bv\rm , \it low\rm , \it high\rm )\rm ) \rm = \rm 1\rm +\it high\rm -\it low\rm )\rm ;

\vspace*{4mm}
\hspace*{0.20in} $\forall$  \rm (\it v1\rm ,\it v2\rm )\rm . \rm (\it v1  $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR  $\land$  \it bv\_size\rm (\it v1\rm ) \rm = \it bv\_size\rm (\it v2\rm )  $\implies$

\hspace*{0.60in}\it bv\_size\rm (\it bv\_and\rm (\it v1\rm , \it v2\rm )\rm ) \rm = \it bv\_size\rm (\it v2\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \rm (\it v1\rm ,\it v2\rm )\rm . \rm (\it v1  $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR\hspace*{0.10in} $\land$  \it bv\_size\rm (\it v1\rm ) \rm = \it bv\_size\rm (\it v2\rm )  $\implies$

\hspace*{0.60in}\rm (\it bv\_and\rm (\it v1\rm , \it v2\rm ) \rm = \it bv\_and\rm (\it v2\rm , \it v1\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \rm (\it v1\rm ,\it v2\rm ,\it v3\rm )\rm . \rm (\it v1  $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR $\land$  \it v3  $\in$  \it BIT\_VECTOR\hspace*{0.10in} $\land$  \it bv\_size\rm (\it v1\rm ) \rm = \it bv\_size\rm (\it v2\rm )  $\land$  \it bv\_size\rm (\it v1\rm ) \rm = \it bv\_size\rm (\it v3\rm )  $\implies$

\hspace*{0.60in}\rm (\it bv\_and\rm (\it v1\rm , \it bv\_and\rm (\it v2\rm ,\it v3\rm )\rm ) \rm = \it bv\_and\rm (\it bv\_and\rm (\it v1\rm , \it v2\rm )\rm , \it v3\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \it bv\rm . \rm (\it bv  $\in$  \it BIT\_VECTOR  $\implies$  \rm (\it bv\_and\rm (\it bv\rm , \it bv\_zero\rm (\it bv\_size\rm (\it bv\rm )\rm )\rm ) \rm = \it bv\_zero\rm (\it bv\_size\rm (\it bv\rm )\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \it bv\rm . \rm (\it bv  $\in$  \it BIT\_VECTOR  $\implies$  \rm (\it bv\_and\rm (\it bv\rm , \it bv\_one\rm (\it bv\_size\rm (\it bv\rm )\rm )\rm ) \rm = \it bv\rm )\rm )\rm ;

\vspace*{4mm}
\hspace*{0.20in} $\forall$  \rm (\it v1\rm ,\it v2\rm )\rm . \rm (\it v1  $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR  $\land$  \it bv\_size\rm (\it v1\rm ) \rm = \it bv\_size\rm (\it v2\rm )  $\implies$

\hspace*{0.60in}\it bv\_size\rm (\it bv\_or\rm (\it v1\rm , \it v2\rm )\rm ) \rm = \it bv\_size\rm (\it v1\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \rm (\it v1\rm ,\it v2\rm )\rm . \rm (\it v1  $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR  $\land$  \it bv\_size\rm (\it v1\rm ) \rm = \it bv\_size\rm (\it v2\rm )  $\implies$

\hspace*{0.60in}\it bv\_size\rm (\it bv\_or\rm (\it v1\rm , \it v2\rm )\rm ) \rm = \it bv\_size\rm (\it v2\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \rm (\it v1\rm ,\it v2\rm )\rm . \rm (\it v1  $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR  $\land$  \it bv\_size\rm (\it v1\rm ) \rm = \it bv\_size\rm (\it v2\rm )  $\implies$

\hspace*{0.60in}\rm (\it bv\_or\rm (\it v1\rm , \it v2\rm ) \rm = \it bv\_or\rm (\it v2\rm , \it v1\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \rm (\it v1\rm ,\it v2\rm ,\it v3\rm )\rm . \rm (\it v1  $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR $\land$  \it v3  $\in$  \it BIT\_VECTOR  $\land$  \it bv\_size\rm (\it v1\rm ) \rm = \it bv\_size\rm (\it v2\rm )  $\land$  \it bv\_size\rm (\it v1\rm ) \rm = \it bv\_size\rm (\it v3\rm )  $\implies$

\hspace*{0.60in}\rm (\it bv\_or\rm (\it v1\rm , \it bv\_or\rm (\it v2\rm ,\it v3\rm )\rm ) \rm = \it bv\_or\rm (\it bv\_or\rm (\it v1\rm , \it v2\rm )\rm , \it v3\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \it bv\rm . \rm (\it bv  $\in$  \it BIT\_VECTOR  $\implies$  \rm (\it bv\_or\rm (\it bv\rm , \it bv\_one\rm (\it bv\_size\rm (\it bv\rm )\rm )\rm ) \rm = \it bv\_one\rm (\it bv\_size\rm (\it bv\rm )\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \it bv\rm . \rm (\it bv  $\in$  \it BIT\_VECTOR  $\implies$  \rm (\it bv\_or\rm (\it bv\rm , \it bv\_zero\rm (\it bv\_size\rm (\it bv\rm )\rm )\rm ) \rm = \it bv\rm )\rm )\rm ;

\vspace*{4mm}
\hspace*{0.20in} $\forall$  \rm (\it v1\rm ,\it v2\rm )\rm . \rm (\it v1  $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR  $\land$  \it bv\_size\rm (\it v1\rm ) \rm = \it bv\_size\rm (\it v2\rm )  $\implies$

\hspace*{0.60in}\it bv\_size\rm (\it bv\_xor\rm (\it v1\rm , \it v2\rm )\rm ) \rm = \it bv\_size\rm (\it v1\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \rm (\it v1\rm ,\it v2\rm )\rm . \rm (\it v1  $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR  $\land$  \it bv\_size\rm (\it v1\rm ) \rm = \it bv\_size\rm (\it v2\rm )  $\implies$

\hspace*{0.60in}\it bv\_size\rm (\it bv\_xor\rm (\it v1\rm , \it v2\rm )\rm ) \rm = \it bv\_size\rm (\it v2\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \rm (\it v1\rm ,\it v2\rm )\rm . \rm (\it v1  $\in$  \it BIT\_VECTOR  $\land$  \it v2  $\in$  \it BIT\_VECTOR  $\land$  \it bv\_size\rm (\it v1\rm ) \rm = \it bv\_size\rm (\it v2\rm )  $\implies$

\hspace*{0.60in}\rm (\it bv\_xor\rm (\it v1\rm , \it v2\rm ) \rm = \it bv\_xor\rm (\it v2\rm , \it v1\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$  \rm (\it bv\rm )\rm . \rm (\it bv  $\in$  \it BIT\_VECTOR  $\implies$  \it bv\_xor\rm (\it bv\rm ,\it bv\rm ) \rm = \it bv\_zero\rm (\it bv\_size\rm (\it bv\rm )\rm )\rm )

\bf END\newpage
\end{sloppypar}\end{document}

>>>>

@@

\hspace*{0.20in}\it BIT\rm ,

\hspace*{0.20in}\it bit\_not\rm ,

\hspace*{0.20in}\it bit\_and\rm ,

\hspace*{0.20in}\it bit\_or\rm ,

\hspace*{0.20in}\it bit\_xor\rm ,

\hspace*{0.20in}\it bool\_to\_bit

@@

\hspace*{0.20in}\it BIT \rm = \rm 0 $\upto$ \rm 1  $\land$

\hspace*{0.20in}\it bit\_not  $\in$  \it BIT  $\fun$  \it BIT  $\land$

\hspace*{0.20in} $\forall$  \rm (\it bb\rm )\rm . \rm (\it bb  $\in$  \it BIT  $\implies$  \it bit\_not\rm (\it bb\rm ) \rm = \rm 1\rm -\it bb\rm )  $\land$

\hspace*{0.20in}\it bit\_and  $\in$  \it BIT  $\times$  \it BIT  $\fun$  \it BIT  $\land$

\hspace*{0.20in} $\forall$  \rm (\it b1\rm , \it b2\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\land$  \it b2  $\in$  \it BIT  $\implies$  \rm (\rm (\it bit\_and\rm (\it b1\rm , \it b2\rm ) \rm = \rm 1\rm )  $\iff$  \rm (\it b1 \rm = \rm 1\rm )  $\land$  \rm (\it b2 \rm = \rm 1\rm )\rm )\rm )  $\land$

\hspace*{0.20in}\it bit\_or  $\in$  \it BIT  $\times$  \it BIT  $\fun$  \it BIT  $\land$

\hspace*{0.20in} $\forall$  \rm (\it b1\rm , \it b2\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\land$  \it b2  $\in$  \it BIT  $\implies$  \rm (\rm (\it bit\_or\rm (\it b1\rm , \it b2\rm ) \rm = \rm 1\rm )  $\iff$  \rm (\it b1 \rm = \rm 1\rm )  $\lor$  \rm (\it b2 \rm = \rm 1\rm )\rm )\rm )  $\land$

\hspace*{0.20in}\it bit\_xor  $\in$  \it BIT  $\times$  \it BIT  $\fun$  \it BIT  $\land$

\hspace*{0.20in} $\forall$  \rm (\it b1\rm , \it b2\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\land$  \it b2  $\in$  \it BIT  $\implies$  \rm (\rm (\it bit\_xor\rm (\it b1\rm , \it b2\rm ) \rm = \rm 1\rm )  $\iff$  \rm (\it b1  $\not =$  \it b2\rm )\rm )\rm )  $\land$

\hspace*{0.20in}\it bool\_to\_bit  $\in$  \bf BOOL  $\fun$  \it BIT  $\land$

\hspace*{0.20in}\it bool\_to\_bit \rm = \rm \{ \bf TRUE  $\mapsto$  \rm 1\rm , \bf FALSE  $\mapsto$  \rm 0 \rm \}

@@

\hspace*{0.20in}\it bit\_not\rm (\rm 0\rm ) \rm = \rm 1\rm ;

\hspace*{0.20in}\it bit\_not\rm (\rm 1\rm ) \rm = \rm 0\rm ;

\hspace*{0.20in} $\forall$ \rm (\it bb\rm )\rm .\rm (\it bb  $\in$  \it BIT  $\implies$  \it bit\_not\rm (\it bit\_not\rm (\it bb\rm )\rm ) \rm = \it bb\rm )\rm ;

\vspace*{4mm}
\hspace*{0.20in}\it bit\_and\rm (\rm 0\rm ,\rm 0\rm ) \rm = \rm 0\rm ;

\hspace*{0.20in}\it bit\_and\rm (\rm 0\rm ,\rm 1\rm ) \rm = \rm 0\rm ;

\hspace*{0.20in}\it bit\_and\rm (\rm 1\rm ,\rm 0\rm ) \rm = \rm 0\rm ;

\hspace*{0.20in}\it bit\_and\rm (\rm 1\rm ,\rm 1\rm ) \rm = \rm 1\rm ;

\hspace*{0.20in} $\forall$ \rm (\it b1\rm ,\it b2\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\land$  \it b2  $\in$  \it BIT  $\implies$  \rm (\it bit\_and\rm (\it b1\rm , \it b2\rm ) \rm = \it bit\_and\rm (\it b2\rm ,\it b1\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$ \rm (\it b1\rm ,\it b2\rm ,\it b3\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\land$  \it b2  $\in$  \it BIT  $\land$  \it b3  $\in$  \it BIT  $\implies$  \rm (\it bit\_and\rm (\it b1\rm , \it bit\_and\rm (\it b2\rm ,\it b3\rm )\rm ) \rm = \it bit\_and\rm (\it bit\_and\rm (\it b1\rm ,\it b2\rm )\rm ,\it b3\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$ \rm (\it b1\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\implies$  \rm (\it bit\_and\rm (\it b1\rm , \rm 1\rm ) \rm = \it b1\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$ \rm (\it b1\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\implies$  \rm (\it bit\_and\rm (\it b1\rm , \rm 0\rm ) \rm = \rm 0\rm )\rm )\rm ;

\vspace*{4mm}
\hspace*{0.20in}\it bit\_or\rm (\rm 0\rm ,\rm 0\rm ) \rm = \rm 0\rm ;

\hspace*{0.20in}\it bit\_or\rm (\rm 0\rm ,\rm 1\rm ) \rm = \rm 0\rm ;

\hspace*{0.20in}\it bit\_or\rm (\rm 1\rm ,\rm 0\rm ) \rm = \rm 0\rm ;

\hspace*{0.20in}\it bit\_or\rm (\rm 1\rm ,\rm 1\rm ) \rm = \rm 1\rm ;

\hspace*{0.20in} $\forall$ \rm (\it b1\rm , \it b2\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\land$  \it b2  $\in$  \it BIT  $\implies$  \rm (\it bit\_or\rm (\it b1\rm , \it b2\rm ) \rm = \it bit\_or\rm (\it b2\rm ,\it b1\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$ \rm (\it b1\rm ,\it b2\rm ,\it b3\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\land$  \it b2  $\in$  \it BIT  $\land$  \it b3  $\in$  \it BIT  $\implies$  \rm (\it bit\_or\rm (\it b1\rm , \it bit\_or\rm (\it b2\rm ,\it b3\rm )\rm ) \rm = \it bit\_or\rm (\it bit\_or\rm (\it b1\rm ,\it b2\rm )\rm ,\it b3\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$ \rm (\it b1\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\implies$  \rm (\it bit\_or\rm (\it b1\rm , \rm 1\rm ) \rm = \rm 1\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$ \rm (\it b1\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\implies$  \rm (\it bit\_or\rm (\it b1\rm , \rm 0\rm ) \rm = \it b1\rm )\rm )\rm ;

\vspace*{4mm}
\hspace*{0.20in}\it bit\_xor\rm (\rm 0\rm ,\rm 0\rm ) \rm = \rm 0\rm ;

\hspace*{0.20in}\it bit\_xor\rm (\rm 0\rm ,\rm 1\rm ) \rm = \rm 1\rm ;

\hspace*{0.20in}\it bit\_xor\rm (\rm 1\rm ,\rm 0\rm ) \rm = \rm 1\rm ;

\hspace*{0.20in}\it bit\_xor\rm (\rm 1\rm ,\rm 1\rm ) \rm = \rm 0\rm ;

\hspace*{0.20in} $\forall$ \rm (\it b1\rm , \it b2\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\land$  \it b2  $\in$  \it BIT  $\implies$  \rm (\it bit\_xor\rm (\it b1\rm , \it b2\rm ) \rm = \it bit\_xor\rm (\it b2\rm ,\it b1\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$ \rm (\it b1\rm ,\it b2\rm ,\it b3\rm )\rm .\rm (\it b1  $\in$  \it BIT  $\land$  \it b2  $\in$  \it BIT  $\land$  \it b3  $\in$  \it BIT  $\implies$  \rm (\it bit\_xor\rm (\it b1\rm , \it bit\_xor\rm (\it b2\rm ,\it b3\rm )\rm ) \rm = \it bit\_xor\rm (\it bit\_xor\rm (\it b1\rm ,\it b2\rm )\rm ,\it b3\rm )\rm )\rm )\rm ;

\hspace*{0.20in} $\forall$ \rm (\it bb\rm )\rm .\rm (\it bb  $\in$  \it BIT  $\implies$  \it bit\_xor\rm (\it bb\rm ,\it bb\rm ) \rm = \rm 0\rm )\rm ;

\vspace*{4mm}
\hspace*{0.20in}\it bool\_to\_bit\rm (\bf TRUE\rm ) \rm = \rm 1\rm ;

\hspace*{0.20in}\it bool\_to\_bit\rm (\bf FALSE\rm ) \rm = \rm 0

\vspace*{4mm}
\bf END\newpage
\end{sloppypar}\end{document}
